An Implementation of the Active Contours without Edges model and the Logic Framework for Active contours on multi-channel images

### 2010-12-13 trunk/cs870/project/Report/Paper.tex
all there but figs not working

@@

\begin{figure*}[t]
\centering
\includegraphics[width=\textwidth]{cvmu.png}
\caption{$\mu$ does not have any effect on the length of the contour. \textit{Salt and pepper} noise was added to the original image for testing purposes. The
figure shows the segmentation for the same image for various values of $\mu$.}
\label{fig:cvmu}
\end{figure*}

@@

\begin{figure*}[t]
\centering
\includegraphics[width=\textwidth]{sccomp.png}
\caption{The complement operator causes the contour to go through an infinite loop between two segmentations: the correct segmentation, and the segmentation
of $A \cap B$.}
\label{fig:sccomp}
\end{figure*}

\subsection{Defining the initial contour ($\phi_0$)}
Both the Chan-Vese model and the Sandberg-Chan model defines the initial contour $\phi_0$ as a signed distance function where $\phi_0$ is positive inside the
contour $C$, zero on the boundary of $C$ (\partial C), and negative outside the contour $C$. Figure [\ref{fig:phinote}] illustrates those assumptions.

>>>>

\begin{figure}[t]
\centering
\includegraphics[width=7cm]{family.png}
\caption{Combining iterations = 7. union 4.01 s intersection 4.12 s}
\label{fig:donutlogic}
\end{figure}

@@

\begin{figure*}[t]
\centering
\includegraphics[width=\textwidth]{cvmu.png}
\caption{$\mu$ does not have any effect on the length of the contour. \textit{Salt and pepper} noise was added to the original image for testing
purposes. Top: original image with noise. Bottom: segmentation for various values of $\mu$.}
\label{fig:cvmu}
\end{figure*}

@@

\begin{figure*}[t]
\centering
\includegraphics[width=\textwidth]{sccomp.png}
\caption{The complement operator causes the contour to go through an infinite loop between two segmentations: the correct segmentation, and the segmentation
of $A_1 \cap A_2$. Bottom: correct and incorrect segmentation respectively}
\label{fig:sccomp}
\end{figure*}

\subsection{Defining the initial contour ($\phi_0$)}
Both the Chan-Vese model and the Sandberg-Chan model defines the initial contour $\phi_0$ as a signed distance function where $\phi_0$ is positive inside the
contour $C$, zero on the boundary of $C$ ($\partial C$), and negative outside the contour $C$. Figure [\ref{fig:phinote}] illustrates those assumptions.
